Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-09 paper/main.tex
updates

\begin{enumerate}
    \item We develop an iterative method based on CI testing to assist researchers in 
	    constructing DAGs using their domain knowledge (Section~\ref{sec:modification}).
    \item We develop a ranking method to prioritize potential modifications in the DAG that 
    	    can help in improving the model's fit quickly (Section~\ref{sec:ranking}).
    \item We provide a web-based interactive tool and a Python package to allow 
	    researchers to easily apply this method to their datasets (Section~\ref{sec:web}).
    \item Lastly, we compare the manual DAG construction method with automated
	    causal discovery algorithms (Section~\ref{sec:empirical}).
\end{enumerate}

>>>>

\begin{enumerate}
    \item We develop an iterative method based on CI testing to assist researchers in 
	    constructing DAGs using their domain expertise (Section~\ref{sec:modification}).
    \item We show a ranking method to prioritize potential modifications to the DAG that 
    	    help in fixing the most severe violations first (Section~\ref{sec:ranking}).
    \item We provide a web-based interactive tool and a Python package to allow 
	    researchers to easily apply this method to their own datasets (Section~\ref{sec:web}).
    \item Lastly, we compare the manual DAG construction method with automated
	    causal discovery algorithms (Section~\ref{sec:empirical}).
\end{enumerate}
